---
title: "mtcars analysis"
author: "Jared Chuang"
date: 2026-09-21
---
# MTCars EDA

Data: [mtcars dataset](https://www.rdocumentation.org/packages/datasets/versions/3.6.2/topics/mtcars), GPL License.

A good idea when starting out with datasets is to get a good feel for the data, see what our data kind of looks like and what rows and columns are in the data.
```{r}
head(mtcars)
```
Next, I want to take a look at the data distribution.
``` {r}
#| label: MTCars Distribution of Fuel Efficiency
#| fig-cap: "Distribution of Fuel Efficiency of Cars"
library(ggplot2)

ggplot(mtcars, aes(x = mpg)) +
  geom_histogram(binwidth = 2, fill = "steelblue", color = "white") +
  labs(
    title = "Distribution of Car Fuel Efficiency",
    x = "Miles per gallon (mpg)",
    y = "Number of cars"
  ) +
  theme_minimal()
```

So first, I separated the data into buckets of 2 mpg to see the distribution of data. From the distribution, the highest number of cars (5) were in the bins [15, 17], [19, 21], and [21, 23]. From the histogram, we can also see that there are not that many cars in the dataset, so this dataset is actually quite small.

Let's confirm.

```{r}
dim(mtcars)
```

We can see there are 32 rows and 11 columns, the dataset is actually very small, we have to keep this in mind when performing any other analysis.


